---
title: "Voting and Postcards"
author: "Surya Fraser"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels) 
library(broom)
```

```{r}
x<-shaming |> 
  mutate(civ_engage = primary_00 + primary_02 + primary_04 + 
                      general_00 + general_02 + general_04) |> 
  select(primary_06, treatment, sex, age, civ_engage) |>
  mutate(
    voter_class = case_when(
      civ_engage %in% c(5, 6) ~ "Always Vote",
      civ_engage %in% c(3, 4) ~ "Sometimes Vote",
      civ_engage %in% c(1, 2) ~ "Rarely Vote"
    ),
    voter_class = factor(voter_class, 
                         levels = c("Rarely Vote", "Sometimes Vote", "Always Vote"),
                         ordered = TRUE)
  )|>mutate(voted=as.factor(primary_06))
```

$$\log\left( \frac{\Pr(Y = 1)}{\Pr(Y = 0)} \right) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_p X_p$$ 

$$\log\left( \frac{\Pr(\text{voted} = 1)}{\Pr(\text{voted} = 0)} \right) = 
\beta_0 + \beta_1 \cdot \text{sex} + \beta_2 \cdot \text{age} + \beta_3 \cdot \text{treatment} + 
\beta_4 \cdot \text{voter\_class} + \beta_5 \cdot (\text{treatment} \times \text{voter\_class})$$

```{r}
 #| cache: true
fit_vote<-logistic_reg(engine = "glm")|>fit(voted ~ sex + age + treatment*voter_class, data = x)|>tidy(conf.int = TRUE)
```

```{r}
library(dplyr)
library(gt)

# Assuming your tibble is named model_tbl
model_tbl <- tibble::tibble(
  term = c("(Intercept)", "age", "sexMale", 
           "treatmentCivic Duty", "treatmentHawthorne", "treatmentSelf", "treatmentNeighbors",
           "voter_classSometimes Vote", "voter_classAlways Vote",
           "treatmentCivic Duty:voter_classSometimes Vote"),
  estimate = c(-2.434345037, 0.012087706, 0.035583881,
               0.086052489, 0.070663507, 0.202358812, 0.358818468,
               0.819714170, 1.608953223,
               0.030789566)
)

# Format the table with gt
model_tbl |>
  mutate(estimate = round(estimate, 3)) |>
  gt() |>
  tab_header(
    title = "Logistic Regression Estimates",
    subtitle = "Predicting Voting Behavior"
  ) |>
  cols_label(
    term = "Term",
    estimate = "Estimate"
  ) |>
  fmt_number(
    columns = estimate,
    decimals = 3
  ) |>
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_column_labels(everything())
  ) |>
  opt_table_outline()

```

```{r}
library(marginaleffects)
library(ggplot2)
library(dplyr)

# Compute marginal effects (difference vs. control)
effects <- predictions(
  fit_vote,
  type = "response",
  by = c("treatment", "group", "voter_class"),
  newdata = datagrid(treatment = unique(x$treatment),
                     voter_class = unique(x$voter_class),
                     group = "all"),
  comparison = "reference",
  reference = "treatment == 'Control'"  # Adjust this if control group is named differently
)

# Filter to only the probability of voting (not not voting)
# If needed, you can also directly subtract predictions manually

# Plot marginal effects
ggplot(effects, aes(x = treatment, y = estimate, fill = voter_class)) +
  geom_col(position = position_dodge(width = 0.7)) +
  facet_wrap(~voter_class) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                position = position_dodge(width = 0.7),
                width = 0.2) +
  labs(
    title = "Treatment Effects on Probability of Voting",
    subtitle = "Compared to Control Group (No Postcard)",
    y = "Change in Probability of Voting",
    x = "Treatment"
  ) +
  theme_minimal() +
  ylim(0, NA)  # Ensures common y-axis across facets

```

During elections, officials are always interested in getting more poeople interested in voting. Using data from the paper "Social Pressure and Voter Turnout: Evidence from a Large-Scale Field Experiment" by Gerber, Green, and Larimer (2008), I attempted to determine "What is the causal effect on voting of receiving a postcard which encourages one to vote?" One possible weakness in this approachis that treatment assignments may not have been randomized, meaning the assumption of unconfoundedness may not hold. I model the effect of sending voters postcards on their decisions to vote in the 2006 with a linear function. Ultimately, the estimate for treatmentCivic Duty was 0.08605249
